Review of Assigned Readings

### 2018-01-04 paper/paper.tex
Update paper.tex
Grammer plus spelling

\subsection{Methodology}
\label{sec:Methodology}
To answer the above mentioned research question a scientific approach has been applied. The paper consists out of three parts. The first part contains an introduction into the topic by pointing out the relevance of the topic, the research question, methodology and the scope. This is conducted in chapter \ref{sec:intro}. The second part is characterized as the theory part. The theory aims to provide the reader with the necessary background information by introducing relevant bitcoin and twitter information in context of the paper. The conducted research is based on forward research and using relevant sources. Furthermore, it contains a short introduction into the Vector Autoregression approach (VAR) and the constrains in context with the paper. This is conducted in chapters \ref{sec:Background} and \ref{sec:EconometricModellingandResults}. The third part contains the discussion of the results and a conclusion. The conclusion is based on the theory and the own conducted mathematical computation. Those computations are based on a data set, which was gathered by own coded python scripts for the timeperiod December 20th - 27th. Based on the short time of observation the results have to be interpreted carefully. The data set contains out of two data sources (1) twitter tweets which contain the buzzword "bitcoin" and (2) historical bitcoin prices. Those two sources has been aggregated with a separate python script. The output of aggregation was further proceeded with stata to conduct the VAR on a daily basis. The third part of the paper is discussed in the chapters \ref{sec:EconometricModellingandResults} and \ref{sec:Conclustion}.

>>>>

\subsection{Methodology}
\label{sec:Methodology}
To answer the above mentioned research question a scientific approach has been applied. The paper consists out of three parts. The first part contains an introduction into the topic by pointing out the relevance of the topic, the research question, methodology and the scope. This is conducted in chapter \ref{sec:intro}. The second part is characterized as the theory part. The theory aims to provide the reader with the necessary background information by introducing relevant bitcoin and twitter information in context of the paper. The conducted research is based on forward research and using relevant sources. Furthermore, it contains a short introduction into the Vector Autoregression (VAR) approach and its constrains in context with the paper. This is conducted in chapters \ref{sec:Background} and \ref{sec:EconometricModellingandResults}. The third part contains the discussion of the results and a conclusion. The conclusion is based on the theory and our mathematical computation. The computation is based on a data set, which was gathered by coded python scripts for the time period December 20th - 27th. Since the results are based on the observation of a short period, they have to be interpreted carefully. The data set consists of two data sources with the following characteristics: (1) twitter tweets which contain the buzzword "bitcoin" and (2) those containing historical bitcoin prices. The two sources has been aggregated with another python script. The output of aggregation was further processed with Stata to conduct the VAR on a daily basis. The third part of the paper is discussed in the chapters \ref{sec:EconometricModellingandResults} and \ref{sec:Conclustion}.
